---
title: "AirBnB Prices"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE, warning = FALSE, message = FALSE)
```


```{r}
library(tidyverse)
library(infer)
library(tidymodels)
library(textrecipes)
library(scales)
library(stacks)
library(tidytext)
theme_set(theme_classic())
```

```{r}
## Load Dataset
set.seed(1234)
train <- read_csv('data/train.csv') %>%
  select(-id)
test <- read_csv('data/test.csv')%>%
  select(-id)
sample <- read_csv('data/sample_submission.csv')

spl <- initial_split(train,prop = 0.75)
train_set <- training(spl)
test_set <-testing(spl)

```


## Exploratory Data Analysis and Feature Engineering


```{r}
train_set %>%
  ggplot(aes(price, fill=neighbourhood_group))+
  geom_histogram(alpha=0.4)+
  scale_x_log10()+
  labs(title = 'Log Distributions price',
       subtitle = 'By Neighbourhood',
       fill = '')
```


This price are log scale with zeros values! Is necessary mutate price in = $log(price)+1$


```{r}

train_set <- train_set %>%
  mutate(log_price = log(price + 1))

test_set <- test_set %>%
  mutate(log_price = log(price + 1))

```

```{r}
train_set %>%
  ggplot(aes(log_price, fill=neighbourhood_group))+
  geom_histogram(alpha=0.6)+
  facet_grid(~neighbourhood_group, scales = 'free_y')
```



I think that is necessary a rutine with inference to understand Bronx and Staten Island 


```{r,fig.height=4}
groups_focus <- c('Bronx','Staten Island')

infer_comparative<-train_set %>%
  filter(neighbourhood_group %in% groups_focus)

infer_comparative %>%
  group_by(neighbourhood,neighbourhood_group)%>%
  count(sort = TRUE)%>%
  ungroup()%>%
  mutate(neighbourhood=fct_reorder(neighbourhood,n))%>%
  ggplot(aes(n,neighbourhood,fill=neighbourhood_group))+
  geom_col()+
  labs(title = 'Comparative Frequence between Bronx and Staten Island',
       fill='')
```


```{r}
infer_comparative %>%
  ggplot(aes(log_price,
             neighbourhood_group,
             fill=neighbourhood_group,
             color=neighbourhood_group))+
  geom_boxplot(alpha=0.4)+
  guides(fill='none',
         color='none')+
  labs(title = '(Log)-Price Comparative between Staten Island and Bronx',
       x = '(log) Price',
       y = '')

```
Between percentile 25th and 75th the similarity levels are most closest in prices.


```{r, fig.height=4}
infer_comparative %>%
  mutate(neighbourhood=fct_reorder(neighbourhood,log_price)) %>%
  ggplot(aes(log_price,
             neighbourhood,
             fill=neighbourhood_group,
             color=neighbourhood_group))+
  geom_boxplot(alpha=0.4)+
  geom_vline(xintercept = mean(infer_comparative$log_price),linetype='dashed')+
  guides(fill='none',
         color='none')+
  labs(title = '(Log)-Price Comparative between Staten Island and Bronx',
       x = '(log) Price',
       y = '')
```

The values has a behaviour very similar into this neighbourhood, for this now is necessary create inferential modelling to understand some effects in this neighbourhood.


```{r}
set.seed(123)
neighb_price<-infer_comparative %>%
  specify(neighbourhood_group~log_price,success = "Bronx")

```

Now that we have different kinds of resampled datasets, we can compute some statistics. Chi test  this is a number that tells us how much difference exists between our observed counts.


```{r}
set.seed(234)

observed_fit <- neighb_price %>%
  specify(log_price~neighbourhood_group)%>%
  fit()

null_fits <-neighb_price %>% 
  specify(log_price~neighbourhood_group) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute")%>%
  fit()

get_confidence_interval(
  null_fits, 
  point_estimate = observed_fit, 
  level = .95
)

visualize(null_fits) + 
  shade_p_value(observed_fit, direction = "both")
```

Low Differences between this neighbourhoods .


```{r}
null_distribution_prices<-neighb_price %>% 
  specify(log_price~neighbourhood_group) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("Staten Island", "Bronx"))


obs_diff_means <- neighb_price %>% 
  specify(log_price~neighbourhood_group) %>%
  calculate(stat = "diff in means", order = c("Staten Island", "Bronx"))

visualize(null_distribution_prices, bins = 10) + 
  shade_p_value(obs_stat = obs_diff_means, direction = "both")
```

```{r}
null_distribution_prices %>% 
  get_p_value(obs_stat = obs_diff_means, direction = "both")
```

This neighbords are the same in prices !




```{r}
summarize_prices <- function(tbl) {
  tbl %>%
    summarize(avg_price = exp(mean(log(price+1))) - 1,
              median_price = exp(median(log(price+1))) - 1,
              n = n()) %>%
    arrange(desc(n))
}

train_set %>%
  group_by(neighbourhood_group) %>%
  summarize_prices() %>%
  mutate(neighbourhood_group = fct_reorder(neighbourhood_group, median_price)) %>%
  ggplot(aes(median_price, neighbourhood_group)) +
  geom_col()
```


## Experimental Design with rooms 



```{r}
train_set %>%
  mutate(room_type = fct_reorder(room_type, price)) %>%
  ggplot(aes(exp(log(price+1)), room_type)) +
  geom_boxplot() +
  scale_x_log10()
```


```{r}
set.seed(1234)
train_set %>%
  sample_n(1000) %>%
  ggplot(aes(minimum_nights + 1, log_price)) +
  geom_point() +
  scale_x_log10() +
  geom_smooth(method = "loess")
```



```{r}

prices<-train_set %>%
  unnest_tokens(word, name) %>%
  group_by(word) %>%
  summarize_prices()

mean(prices$avg_price)

train_set %>%
  unnest_tokens(word, name) %>%
  group_by(word) %>%
  summarize_prices() %>%
  head(60) %>%
  mutate(word = fct_reorder(word, avg_price)) %>%
  ggplot(aes(avg_price, word, size = n, color=avg_price>median(prices$avg_price))) +
  geom_point(show.legend = FALSE)+
  geom_vline(xintercept = median(prices$avg_price),color='gray',linetype='dashed')+
  labs(title = 'Comparative Prices by Descriptions',
       x='Log Prices')
```


```{r}
train_set %>%
  ggplot(aes(last_review, log(price+1))) +
  geom_point() +
  geom_smooth(method = "lm")
```

## Model 

```{r}
set.seed(2022)
mset <- metric_set(rmse,mae)
grid_control <- control_grid(save_pred = TRUE,
                             save_workflow = TRUE,
                             extract = extract_model)
train_fold <- train_set %>%
  vfold_cv(10)


prep_juice <- function(d) juice(prep(d))
xg_rec <- recipe(price ~ minimum_nights + room_type + number_of_reviews +
                   latitude + longitude + neighbourhood_group +
                   reviews_per_month + calculated_host_listings_count +
                   availability_365 + last_review,
                 data = train_set) %>%
  step_mutate(is_manhattan = neighbourhood_group == "Manhattan") %>%
  step_rm(neighbourhood_group) %>%
  step_mutate(last_review = coalesce(as.integer(Sys.Date() - last_review), 0)) %>%
  step_dummy(all_nominal_predictors())


xg_mod <- boost_tree("regression",
                     mtry = tune(),
                     trees = tune(),
                     learn_rate = tune()) %>%
  set_engine("xgboost")

xg_wf <- workflow() %>%
  add_recipe(xg_rec) %>%
  add_model(xg_mod)

xg_tune <- xg_wf %>%
  tune_grid(train_fold,
            metrics = mset,
            control = grid_control,
            grid = crossing(mtry = c(1:7),
                            trees = seq(250, 1500, 25),
                            learn_rate = c(.008, .01)))

autoplot(xg_tune)

xg_fit <- xg_wf %>%
  finalize_workflow(select_best(xg_tune)) %>%
  fit(train)

xg_fit %>%
  augment(test_set) %>%
  mutate(.pred=log(.pred+1))%>%
  ggplot(aes(log_price,.pred))+
  geom_point(alpha=0.4)+
  geom_abline(color='blue')+
  labs(title = 'Comparative values with XGboost Model')

```

```{r}
importances <- xgboost::xgb.importance(model = xg_fit$fit$fit$fit)

importances %>%
  mutate(Feature = fct_reorder(Feature, Gain)) %>%
  ggplot(aes(Gain, Feature)) +
  geom_col()

```

